### 2023-11-01 thesis/sections/5-grounding.tex
evaluation

The model achieves almost perfect accuracy on the 'Dale-2' dataset with 99\%.
For both other datasets, the accuracy is slightly lower with 94\% and 93\% respectively, but still close to perfect, especially compared to the random baseline.
First, this shows that the model is able to extract attribute features from the image and manages to combine them with the given information about the target object.
This worsens slightly, when more objects are introduced.
More objects lead to more needed attributes to discriminate the objects from each other.
The model is still able to extract and utilize these additional attributes and combine them with the given attribute encoding of the target object.
The model can generate these high results, even with its relatively simple architecture.
In this architecture, the model doesn't compare the objects directly to each other, but each object is only associated with the attribute encodings.
A more complex architecture, in which the model is additionally tasked to discriminate the objects directly from each other might even improve the results.
% SD: The model is able to leatn to discriminate objects based on visual appearance.
% DK: TODO

>>>>

                                        &                           & \multicolumn{3}{c}{\textbf{dale-5}} & \multicolumn{3}{c}{\textbf{dale-2}} & \multicolumn{3}{c}{\textbf{colour}}                                                                                                                                                             \\  \cmidrule(lr){3-5}\cmidrule(lr){6-8}\cmidrule(lr){9-11}
        coordinate-classifier-dimension & image-embedding-dimension & \textbf{accuracy}                   & \textbf{word-by-word-f1}            & \textbf{non-target-accuracy}        & \textbf{accuracy} & \textbf{word-by-word-f1} & \textbf{non-target-accuracy} & \textbf{accuracy} & \textbf{word-by-word-f1} & \textbf{non-target-accuracy} \\\midrule
        {10}                            & {1500}                    & {33\%}                              & {67,47\%}                           & {14\%}                              & {84\%}            & {81,42\%}                & {4\%}                        & {12\%}            & {33,43\%}                & {34\%}                       \\
        {10}                            & {2000}                    & {36\%}                              & {69\%}                              & {13\%}                              & {83\%}            & {82,89\%}                & {4\%}                        & {13\%}            & {36\%}                   & {34\%}                       \\
        {10}                            & {3000}                    & {34\%}                              & {68\%}                              & {12\%}                              & {82\%}            & {79,89\%}                & {4\%}                        & {12\%}            & {32,31\%}                & {34\%}                       \\
        {15}                            & {1500}                    & {35\%}                              & {68,99\%}                           & {12\%}                              & {85\%}            & {84,43\%}                & {4\%}                        & {17\%}            & {38,49\%}                & {31\%}                       \\
        {15}                            & {2000}                    & {34\%}                              & {67\%}                              & {14\%}                              & {84\%}            & {81,89\%}                & {4\%}                        & {14\%}            & {33,31\%}                & {33\%}                       \\
        {15}                            & {3000}                    & {32\%}                              & {65,5\%}                            & {15\%}                              & {85\%}            & {81,89\%}                & {4\%}                        & {13\%}            & {32,73\%}                & {35\%}                       \\
        {30}                            & {1500}                    & {36\%}                              & {68,99\%}                           & {15\%}                              & {84\%}            & {80,95\%}                & {4\%}                        & {14\%}            & {36,97\%}                & {33\%}                       \\
        {30}                            & {2000}                    & {32\%}                              & {65,5\%}                            & {16\%}                              & {85\%}            & {82,95\%}                & {4\%}                        & {18\%}            & {39\%}                   & {32\%}                       \\
        {30}                            & {3000}                    & {3\%}                               & {63,5\%}                            & {16\%}                              & {83\%}            & {80,89\%}                & {3\%}                        & {12\%}            & {32,73\%}                & {34\%}                       \\
        {100}                           & {10}                      & {21\%}                              & {57\%}                              & {23\%}                              & {16\%}            & {37\%}                   & {31\%}                                                                                                     \\
        {100}                           & {15}                      & {17\%}                              & {52,98\%}                           & {25\%}                              & {78\%}            & {71,99\%}                & {11\%}                       & {26\%}            & {43,49\%}                & {3\%}                        \\
        {100}                           & {30}                      & {19\%}                              & {54,46\%}                           & {24\%}                              & {68\%}            & {42,79\%}                & {4\%}                        & {29\%}            & {45,49\%}                & {26\%}                       \\
        {500}                           & {10}                      & {27\%}                              & {61,98\%}                           & {16\%}                              & {83\%}            & {79,95\%}                & {6\%}                        & {17\%}            & {38,49\%}                & {32\%}                       \\
        {500}                           & {15}                      & {28\%}                              & {63,5\%}                            & {16\%}                              & {83\%}            & {79,5\%}                 & {7\%}                        & {21\%}            & {4\%}                    & {31\%}                       \\
        {500}                           & {30}                      & {3\%}                               & {63,98\%}                           & {17\%}                              & {84\%}            & {83,43\%}                & {5\%}                        & {21\%}            & {4\%}                    & {31\%}                       \\
        {1000}                          & {10}                      & {31\%}                              & {65,5\%}                            & {13\%}                              & {84\%}            & {82,42\%}                & {5\%}                        & {12\%}            & {32,12\%}                & {34\%}                       \\
        {1000}                          & {15}                      & {31\%}                              & {64,5\%}                            & {16\%}                              & {85\%}            & {82,42\%}                & {5\%}                        & {16\%}            & {37\%}                   & {32\%}                       \\
        {1000}                          & {30}                      & {31\%}                              & {63,98\%}                           & {17\%}                              & {85\%}            & {82,81\%}                & {4\%}                        & {13\%}            & {36\%}                   & {34\%}                       \\
    \caption{test}
    \label{test}
The model achieves almost perfect accuracy on the 'Dale-2' dataset with 99\%.
For both other datasets, the accuracy is slightly lower with 94\% and 93\% respectively, but still close to perfect, especially compared to the random baseline.
First, this shows that the model is able to extract attribute features from the image and manages to combine them with the given information about the target object.
This worsens slightly, when more objects are introduced.
More objects lead to more needed attributes to discriminate the objects from each other.
The model is still able to extract and utilize these additional attributes and combine them with the given attribute encoding of the target object.
The model can generate these high results, even with its relatively simple architecture.
In this architecture, the model doesn't compare the objects directly to each other, but each object is only associated with the attribute encodings.
A more complex architecture, in which the model is additionally tasked to discriminate the objects directly from each other might even improve the results.
% SD: The model is able to leatn to discriminate objects based on visual appearance.
% DK: TODO
